
<!-- README.md is generated from README.Rmd. Please edit that file -->

# ATCapiR `r badger::badge_custom("dev version", as.character(packageVersion("ATCapiR")), "blue", "https://github.com/PatrickRWright/ATCapiR")` [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/PatrickRWright/ATCapiR?branch=master&svg=true)](https://ci.appveyor.com/project/PatrickRWright/ATCapiR) [![travis](https://api.travis-ci.com/PatrickRWright/ATCapiR.svg?branch=master)](https://api.travis-ci.com/PatrickRWright/ATCapiR.svg?branch=master) [![codecov](https://codecov.io/github/PatrickRWright/ATCapiR/branch/master/graphs/badge.svg)](https://codecov.io/github/PatrickRWright/ATCapiR)

## Before you install

If you would like to work with this package you will first need to create a personal account at
the [NCBI Bioportal](https://bioportal.bioontology.org/). Withing your account information you should
be able to find an API key. Only a valid API key will allow you to use the package.

## Installing from GitHub with devtools

```{r, eval = FALSE}
devtools::install_github("PatrickRWright/ATCapiR")
```

## Basic usage

```{r, echo = TRUE, warning=FALSE, message=FALSE, eval = FALSE}
# load the package
library(ATCapiR)
# vector of ATC codes
ATC_vect <- c("A02BC02", "C03BA08", "A02BC02", "A02BC02", "A07DA03", "A07DA03",
              "A02BC02", "A02BC02", "A02BC02", "A02BC02", "C10AA05", "C10AA05",
              "C10AA05", "N05BA06", "N05BA06", "N05BA06", "N06AX11", "N06AX11")
# you will need to create an account at https://bioportal.bioontology.org/ to receive an api_key
# the key below is not real and just supposed to give you an impression of the format
api_key <- "a123b456-cd78-91e2-fgh3-4ij56kl7mno8"
# return translation at third level resolution
ATC_translated_df <- translate_ATC_codes(ATC_vect, level_depth = 3, api_key = api_key)
```

If `HTTP error 401` is returned your API key is likely wrong or void.